proof-of-concept_mods

### 2023-10-27 proof-of-concept_mods.Rmd
gam parser, visualize results

## Load Data

@@

Designate *basic* model formula

@@

Check sex's significance in variance

```{r}
K <- drop1(basic.m1, what="sigma", scope = "sex")
class(K)
K["Pr(Chi)"]
K$"Pr(Chi)"[2]

test.mu <- drop1(basic.m1, what="mu", scope = "sex")
test.sig <- drop1(basic.m1, what="sigma", scope = "sex")

#write for testing
saveRDS(basic.m1, file="/Users/megardn/Desktop/BGD_Repos/combat_biovar/gamlss_basic_test_mod.rds")

get.and.drop1.p("/Users/megardn/Desktop/BGD_Repos/combat_biovar/gamlss_basic_test_mod.rds", moment="sigma", term="sex")

test.model.list <- c()
test.model.list[[1]] <- basic.m1
lapply(test.model.list, drop1, what="mu", scope = "sex")
```

## Review Results

@@

No.

@@

##Troubleshooting

Troubleshooting drop1

```{r}
model.test <- readRDS("~/Desktop/BGD_Repos/combat_biovar/ukb_basic/lh_SA_superiortemporal_ukb-CN-data-simsites_mod.rds")
drop1(model.test, what = "sigma")
model.test.drop <- gamlss(formula = lh_SA_superiortemporal ~ poly(age_days, 3) + sex,
                       sigma.formula = ~ poly(age_days, 3),
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)
drop1(model.test.drop, what = "sigma")

ukb_df_age.filt <- ukb_df_age.filt %>%
  mutate(sexMale = as.numeric(case_when(sex == "Male" ~ 1,
                                        sex == "Female" ~ 0,
                                        TRUE ~ NA)))
model.test.refit <- gamlss(formula = lh_SA_superiortemporal ~ poly(age_days, 3) + sexMale,
                       sigma.formula = ~ poly(age_days, 3) + sexMale,
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)
drop1(model.test.refit, what = "sigma", scope = "sexMale")

model.test.refit2 <- gamlss(formula = lh_SA_superiortemporal ~ poly(age_days, 3) + sex,
                       sigma.formula = ~ poly(age_days, 3) + sex,
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)

drop.test.obj<-drop1(model.test.refit2, what = "nu")
df <- drop.test.obj %>%
  as.data.frame() %>%
  mutate(what=attributes(drop.test.obj)$heading[2]) %>%
  add_rownames(var = "term")

f <- drop1_all(model.test.refit2, name="TEST")
```

```{r}
# Your input string
input_string <- "xxxx ref.batch = yyyy"

# Check if the input string contains "ref.batch =" using a regular expression
if (grepl("ref\\.batch\\s*=\\s*", input_string)) {
  # Your code for splitting the string
  # Split the string into two parts
  split_string <- unlist(strsplit(input_string, "ref.batch", fixed = TRUE))

  # The split_string will contain two elements
  part1 <- split_string[1]
  part2 <- gsub("=", "", split_string[2])

  # Trim any leading/trailing white spaces in part2
  part2 <- trimws(part2)

  # Output the two parts
  print(part1)
  print(part2)
} else {
  cat("The input string does not contain 'ref.batch ='\n")
}
```

>>>>

# Analysis Outline
## Load Data

@@

## Basic Models
Designate *basic* model formula

@@

# Review Results

@@

No.ln

@@
